---
title: "p8105_hw3_rm3609"
author: "Runqi Ma"
date: "2018/10/14"
output: html_document
---


```{r}
library(tidyverse)
library(patchwork)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

#Problem 1 
###First, do some data cleaning:
format the data to use appropriate variable names;
focus on the “Overall Health” topic
include only responses from “Excellent” to “Poor”
organize responses as a factor taking levels ordered from “Excellent” to “Poor”

```{r}
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
data(brfss_smart2010)

brfss_smart2010 = janitor::clean_names(brfss_smart2010) %>% 
  rename(resp_id = respid, state = locationabbr, location = locationdesc) %>% 
  filter(topic == "Overall Health", 
         response %in% c("Excellent","Very good","Good","Fair","Poor"))


mutate(brfss_smart2010,response = as.factor(response)) %>% 
  mutate(response = forcats::fct_relevel(response, c("Excellent", "Very good", "Good", "Fair", "Poor")))

```


###In 2002, which states were observed at 7 locations?
```{r}
brfss_smart2010 %>% 
  filter(year == 2002) %>% 
  group_by(state) %>% 
  summarize(n = n_distinct(location)) %>% 
  filter(n == 7)
  
```

###Make a “spaghetti plot” that shows the number of locations in each state from 2002 to 2010.
```{r}
brfss_smart2010 %>% 
  filter(year %in% c(2002:2010)) %>% 
  group_by(state, year) %>% 
  summarize(n = n_distinct(location)) %>% 
  ggplot(aes(x = year, y = n, color = state), alpha = .5) +
  geom_line() +
   labs(
    title = "Location Number in Each State",
    x = "year",
    y = "number of locations"
  ) + 
  theme_bw()
  
```

###Make a table showing, for the years 2002, 2006, and 2010, the mean and standard deviation of the proportion of “Excellent” responses across locations in NY State.
```{r}
brfss_smart2010 %>% 
  filter(year %in% c(2002, 2006, 2010), state == "NY", response == "Excellent" ) %>%
  group_by(year) %>% 
  summarize(mean = mean(data_value),
            sd = sd(data_value)) %>% 
  knitr::kable()
```

###For each year and state, compute the average proportion in each response category (taking the average across locations in a state). Make a five-panel plot that shows, for each response category separately, the distribution of these state-level averages over time.
```{r}
brfss_smart2010 %>% 
  group_by(state, year, response) %>% 
  summarize(prop_mean = mean(data_value)) %>% 
  ggplot(aes(x = year, y = prop_mean, color = state)) +
  geom_point(alpha = .5) +
  facet_grid(~response) +
   labs(
    title = "Average proportion in each response category",
    x = "Year",
    y = "Average proportion"
  ) + 
  theme_bw()
```

#Problem 2



###How many aisles are there, and which aisles are the most items ordered from?
```{r}
insta = instacart %>% janitor::clean_names() 

insta %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

There are 134 aisles. Fresh vegetables are the most items.

###Make a plot that shows the number of items ordered in each aisle. Order aisles sensibly, and organize your plot so others can read it.
```{r}
insta %>% 
  group_by(aisle) %>% 
  summarize(n = n()) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_point()
```

###Make a table showing the most popular item in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”.
```{r}
insta %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>%
  count(product_name) %>%
  filter(n == max(n)) %>% 
  knitr::kable()
```

###Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
insta %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  mutate(order_dow = 
           factor(order_dow, labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))) %>% 
  group_by(product_name, order_dow) %>%
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  spread(key = order_dow, value = mean_hour) %>% 
  knitr::kable()
```


#Problem 3

```{r}
skimr::skim(ny_noaa)
```

###Do some data cleaning. Create separate variables for year, month, and day. Ensure observations for temperature, precipitation, and snowfall are given in reasonable units. For snowfall, what are the most commonly observed values? Why?

```{r}
noaa = ny_noaa %>% 
  separate(date, into = c("year", "month", "day"), sep = "-") %>% 
  mutate(
    tmax = as.numeric(tmax)/10, 
    tmin = as.numeric(tmin)/10, 
    prcp = as.numeric(prcp)/10, 
    snow = as.numeric(snow)/10,
    snwd = as.numeric(snwd)/10)
  
noaa %>% 
  count(snow) %>% 
  arrange(desc(n))
```


###Make a two-panel plot showing the average max temperature in January and in July in each station across years. Is there any observable / interpretable structure? Any outliers?
```{r}
noaa %>% 
  filter(month %in% c("01", "07") & is.na(tmax) == FALSE) %>% 
  group_by(month, id, year) %>% 
  summarize(aver_maxt = mean(tmax,na.rm = TRUE)) %>% 
  ggplot(aes(x = year, y = aver_maxt), color = id) +
  geom_boxplot() +
  facet_grid(~month) +
   labs(
    title = "Average Max Temperature in January and in July",
    x = "Year",
    y = "Average Max Temperatur"
  ) + 
  theme_bw()
  
```

###Make a two-panel plot showing (i) tmax vs tmin for the full dataset (note that a scatterplot may not be the best option) (ii) make a plot showing the distribution of snowfall values greater than 0 and less than 100 separately by year.
```{r}


dist_snow = 
  noaa %>% 
  filter(snow > 0 & snow < 10) %>% 
  ggplot(aes(x = year, y = snow)) +
  geom_violin()
 dist_snow 
 

```

